Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-06 Paper/grass.tex
Improved discussion and conclusion
The comparison with frequency is dealt with first so as to combine the discussion of the threshold into one coherent section. The note about disagreement due to variation of grass density and eddy viscosity with depth is moved to a paragraph on limitations near the end of the paper. And the conclusion is improved to summarize the paper.

@@

Comparison of frequency (Im$(\sigma)$) of the fastest growing mode with that of experimental observations of frequencies in the lab scale experiments, for cases where the vegetation was sufficiently dense to be modeled by a continuum drag field, is also shown in Figure \ref{Re_vs_delta}. 
The observed frequencies are associated with the peaks in velocity spectra, frequency of monami and frequency of vortex passage \cite{Ghisal02}, and compare well with the predicted frequencies. 
The deviation of predicted frequency from the observed may be attributed to the various simplification we have made in our model. 
In a real canopy, the drag coefficients are known to vary from bottom to tip of the grass blades\cite{Vivoni98,Nepf00}. The turbulent viscosity is also known to vary between the flow of unvegetated region and flow through the canopy\cite{Ghisal02}. 
Although these variation are not central to the mechanism leading to the instability of flow, we believe an improved analysis of flow with these variation in the model might lead to a better agreement between the observed frequency and the predicted frequency.

@@

In conclusion we note that linear stability analysis of flow in presence of canopy reveals the existence of a threshold flow for the onset of the instability.
%two distinct modes of flow instability. 
The occurrence of these modes for flow instability in a canopy depends on its submergence ratio and shear layer thickness. Our analysis predict a threshold criteria characterized by a Reynolds number. 
The predicted value of threshold Reynolds number agrees well with experimentally observed parameters. 
Inclusion of variation of drag coefficient along the grass filament might lead to better agreement between the observed and predicted frequency of monami. 
Our analysis also informs flow structure formation in many other related scenarios, such as flow over coral reefs, permeable sediments, etc. and therefore is expected to have a wider impact.

>>>>

Comparison of frequency (Im$(\sigma)$) of the fastest growing mode with that of experimental observations of frequencies in the lab scale experiments, for cases where the vegetation was sufficiently dense to be modeled by a continuum drag field, is also shown in Figure \ref{Re_vs_delta}. 
The observed frequencies are associated with the peaks in velocity spectra, frequency of monami and frequency of vortex passage \cite{Ghisal02}, and compare well with the predicted frequencies.

@@

@@

The deviation of our model predictions from the observed may be attributed to the various simplification we have made in our model. 
In a real canopy, the drag coefficients are known to vary from bottom to tip of the grass blades\cite{Vivoni98,Nepf00}. 
The turbulent viscosity is also known to vary between the flow of unvegetated region and flow through the canopy\cite{Ghisal02}. 
Although an improved analysis of flow with these variation in the model might lead to a better agreement between the observed and the predicted quantities, these variation are not central to the mechanism leading to the instability of flow.

In conclusion, we note that the threshold flow condition observed in the field and in lab experiments arises due to the presence of vegetation drag. We show the origin of this threshold using a consistent continuum hydodynamic stabiity analysis for the shear flow that develops as a result of the drag. Such an analysis not only explains quantitative observations, but also provides an understanding of the hydrodynamic instability mechanism. The extent of the structure of Mode 2 throughout the depth of the water column implies an efficient transport of suspended tracers compared to that due to the localized structure of Mode 1 near the canopy top. 
Our analysis also informs flow structure formation in many other related scenarios, such as flow over coral reefs, permeable sediments, etc. and therefore is expected to have a wider impact.
